%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\noBoldItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://danvanhorn.github.io./}{\Large Daniel Van Horn}} & Email : \href{mailto:vanhornd@oregonstate.edu}{vanhornd@oregonstate.edu}\\
  \href{http://danvanhorn.github.io/}{https://danvanhorn.github.io} & Mobile : 971-237-4103 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oregon State University}{Corvallis, OR}
      {Bachelor of Science in Computer Science, Computer Systems;  GPA: 3.50}{Sep. 2015 -- Jun. 2019}
    \resumeSubheading
      {Chemeketa Community College}{Salem, OR}
      {Associate of Arts;  GPA: 3.26}{Aug. 2013 -- July. 2015}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
     \textbf{Languages}{: \textbf{C#, C++, C, JavaScript, HTML, CSS,} LESS, JSON, SQL, MySql, Node JS, Python, Java, XML, YAML}}
     \item{
      \textbf{Technologies}{: \textbf{React Js, Typescript, NPM, Redux, Flux, Webpack,} Babel, JQuery, Bootstrap, Razor, XSLT}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Center For Applied Systems and Software}{Corvallis, OR}
      {Software Engineer}{May 2016 - Present}
      \resumeItemListStart
        \resumeItem{Smarter Balanced}
          {Suite of C\# and Node Js microservice applications with a shared component library in React Js and Typescript for the Smarter Balanced Assessment Consortium. Minimized repeated code and allowed for thorough automated testing and continuous integration. Singlehandedly increased code coverage from 0 to 80\%.}
        \resumeItem{Oregon Department of Transportation}
          {Developed RESTful geospatial web services to supply dynamic geo-spatial information to MVC web applications in C\# with a SQL back end. Parsed user input from various inputs to dynamically render data-driven graphics on screen.}
      \resumeItemListEnd

    \resumeSubheading
      {CDK Global}{Portland, OR}
      {Software Engineer Intern}{June 2017 - September 2017}
      \resumeItemListStart
        \resumeItem{Customer Search Interface}
          {Designed and implemented a user interface in React Js for a search search interface. Instituted a workflow for developers to follow; automated testing, building, and publishing to NPM.}
        \resumeItem{Cloud Search}
          {Member of winning team in the 2017 CDK Global Hackathon. Created a cloud service for indexing the entire customer database. Increased search speeds by a factor of fifty which was estimated to save the company over \$8 million a year in computation time.}
      \resumeItemListEnd

    \resumeSubheading
      {OSU School of Electrical Engineering and Computer Science}{Corvallis, OR}
      {Data Scientist}{Summer 2012 and 2013}
      \resumeItemListStart
        \noBoldItem{Taught students foundational skills in UNIX, Python, C++ and object oriented programming during weekly lecture sessions.}
        \noBoldItem{Provided tutoring services regarding design, programming and debugging issues students face both in face-to-face and remote sessions.}
        \noBoldItem{Collaborated with faculty to develop new curriculum and assignments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{SB-Components}
      {A shared component library in React Js and Typescript, tested and published to NPM using TravisCI.}
    \resumeSubItem{AP Score Guide}
      {Standardized testing application built to query, sort and generate pdf files based on test items.}
  \resumeSubHeadingListEnd

\end{document}
