%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\noBoldItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://tnoelcke.github.io./}{\Large Thomas Noelcke}} & Email : \href{mailto:noelcket@oregonstate.edu}{noelcket@oregonstate.edu}\\
  1170 S9th St. Lebanon, OR 97335 & Mobile : 971-645-1311 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Center For Applied Systems and Software}{Corvallis, OR}
      {Software Developer}{May 2017 - Present}
      \resumeItemListStart
					\resumeItem{ODOT Response Planning}{Suite of C\#, WinForms, and WPF application that creates dynamic messages for message signs on roads. Created WCF services that communicate with external services.}
					\resumeItem{ODOT Trip Check Local Entry}{Created interactive prototype of an application that allows entry of road events from municipalities. Met with clients to determine basic application requirements.}
					\resumeItem{ODOT Resource Management}{Worked with a team to provide QA and bug fixes for a C\#, Knockout.js, and WinForms application. Ran manual test cases, wrote unit tests and implemented bug fixes.}
      \resumeItemListEnd
			
			
	    \resumeSubheading
			{OSU School of Business}{Corvallis, OR}
			{Teaching Assistant}{September 2017 - December 2017}
			\resumeItemListStart
				\resumeItem{Office Hours}{Held office hours where I helped students learn about general programming practices, answered questions about assignments and quizzes.}
				\resumeItem{Curriculum}{Collaborated with instructor to develop curriculum including assignments, quizzes and exams.}
				\resumeItem{Grading}{Evaluated student work based on a rubric.}
			\resumeItemListEnd
			\resumeSubheading
				{OSU College of Mechanical Engineering Management}{Corvallis, OR}
				{Technical Assistant}{June 2017 - December 2017}
				\resumeItemListStart
						\resumeItem{Kiosk}{Updated a HTML and JavaScript application to display slide shows on a kiosk out side the CEM office.}
						\resumeItem{Excel}{Provided help on excel projects including writing automated scripts in VBA to calculate desired results.}
				\resumeItemListEnd
		\resumeSubheading
		    {Guardian Real Estate Services}{Portland, OR}
		    {Maintenance Technician}{September 2013 - August 2016}
		    \resumeItemListStart
		        \resumeItem{Work Orders}{Worked directly with tenants to discover and address maintenance concerns.}
		        \resumeItem{Apartment Turns}{Inspected apartments for wear and damage. Implemented repairs and worked with vendors to ensure apartments were ready for new move ins.}
            \resumeItemListEnd
        
        \resumeSubheading
            {St.Helens High School}{St.Helens, OR}
            {Head Tennis Coach}{February 2013 - July 2014}
            \resumeItemListStart
                \resumeItem{Coaching}{Designed tennis program to maximize team and individual development.}
                \resumeItem{Administration}{Communicated with parents, teachers, and administration. Organized team of volunteers to run practices.}
            \resumeItemListEnd
		    
		    
  \resumeSubHeadingListEnd
  
  %--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
     \textbf{Languages}{: \textbf{C\#, C++, C, JavaScript, JSON, Java, HTML, CSS, Python,} SQL, XML, XAML, Bootstrap, VBA, LaTex, Node JS, Bash, YAML}}
     \item{
      \textbf{Technologies}{: \textbf{Razor, ASP.NET MVC, NPM} AngularJS, Django, Visio, JQuery, Bootstrap, WPF, WCF}
    }
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oregon State University}{Corvallis, OR}
      {Bachelor of Science in Computer Science, Business Option:  GPA: 3.63}{Sep. 2016 -- Dec. 2018}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{AgBiz-Logic}
      {A Django Backend with Angular Fontend and a Postgres SQL databse.}
    \resumeSubItem{Tocs: Response Planing}
      {Sub module of ODOT's TOCS application that produces automated messages for messages signs based on event parameters.}
  \resumeSubHeadingListEnd
\end{document}
